---
title: "Karplus-Strong Algorithm"
author: "Angelo Nardone"
date: "January 30, 2015"
output: html_document
---

```{r, echo=FALSE, plot_dsp_style}
plot_dsp_style <- function(x)
{
    plot(x,type="h")
    points(x,type="p")
    abline(h=0,col="red")
}

```
Let's explore the R code implementing the equation

$y[n]= \alpha y[n-M]+x[n],$

where x[n] is the input signal, M is the delay, and α is the decay. 
We assume that the value of the delay M is equal to the length of the input signal x. 
In words, it is like filling the delay buffer and then recursively going over it. 
Additionally, we set the length of the output to be a multiple of the delay M (i.e., of the length of the input signal). 
This is controlled by the argument D, so that the output length is D∗M.

```{r ks_loop}
ks_loop <- function(x,alpha,D)
{
    if (D <= 0) stop ("D has to be bigger than 0 (cero)")
    if (length(x)<=1) stop("x should be a secuence of data biger than 1")
    
    M <- length(x)
    size_y <- D * M
    y <- x
    
    for (i in M:size_y)
    {
        # we add the 1 because in R the vectors starts with the index 1
        y[i] <- alpha * y[i-M +1]
    }
    return(y)
}
```


First let's crate a random sequece of 100 and plot it
```{r}
x <-rnorm(100)
# plot random data
plot_dsp_style(x)
```

And now let's apply the <b> ks_loop </b> algorithm

```{r}
# apply ks_loop algorithm
ks <- ks_loop(x, .9, 10)
# plot the KS applied to the random generated data
plot_dsp_style(ks)
```



